Application of convolutional neural networks in optical text recognition to junk data filtering

### 2021-06-24 tex/paper/OMFI2021_Razumov_paper.tex
Minor changes
Style of ref and tables was updated.

\begin{abstract}
In this paper, the problem of constructing a model for detecting and filtering unwanted spam messages is solved. A fully connected convolutional neural network ({FCNN}) was chosen as the model of the classifier of unwanted emails in email. It allows you to divide emails into two categories: \emph{spam} and \emph{not spam}.
The main result of the research is a software application in the \textsf{C++} language, which has a micro-service architecture and solves the problem of image classification. The app can handle more than $10^6$ requests per minute in real-time.
\end{abstract}

@@

\begin{table}[h!]
	\centering
	\caption{\label{tbl:01}Training result}
	\begin{center}
		\begin{tabular}{lcc}
			\mr
			embeddings & precision & recall \\
			\mr
			BOW & 0.91143 & 0.99961 \\ \hline
			Fast Text & \bf 0.95523 & \bf 0.89164 \\ 
			\mr
		\end{tabular}
	\end{center}
\end{table}

@@

\begin{table}[h!]
	\centering
	\caption{\label{tbl:02}Training result}
	\begin{center}
		\begin{tabular}{lcc}
			\mr
			embeddings & precision & recall \\
			\mr
			BOW & 0.93604 & 0.95643 \\ \hline
			Fast Text & \bf 0.99931 & \bf 0.91263 \\ 
			\mr
		\end{tabular}
	\end{center}
\end{table}

@@

\section*{References}
\begin{thebibliography}{99}
\bibitem{Makkar2021} 
Aaisha M, Uttam G, Pradip K S
2021 {Artificial intelligence and edge computing--enabled
web spam detection for next generation IoT
applications} {\it IEEE Sensors Journal} {\bf } pp 1--9

\bibitem{Taylor2020}
Taylor O E, Ezekiel P S
2020 {A model to detect spam email using support vector classifier and random forest classifier} 
\emph{Int. J. Comput. Sci. Math. Theory} {\bf 6} 1 pp 1--11

\bibitem{Garg2021}
Pranjul G, Nancy G
2021 {A systematic review on spam filtering techniques based on
natural language processing framework} \emph{2021 11th International Conference on Cloud Computing, Data Science \& Engineering (Confluence 2021)} pp 30--35

\bibitem{Parmar2020}
Nandan P, Ankita S, Harshita J, Amol K K
2020 {Email spam detection using naïve Bayes and particle swarm optimization} \emph{Int. J. Inn. Res. Tech.} {\bf 6} 10 pp 367--373

\bibitem{Mohammad2020}
Mohammad RMA
2020 \emph{A lifelong spam emails classification model}
\emph{Appl. Comp. and Inf.} pp 1--20

\bibitem{Mikolov2013} 
Mikolov T, Chen K, Corrado G, and Dean J
2013 {Efficient estimation of word representations in vector space} 
arXiv:1301.3781v3

\bibitem{Bojanowski2017} 
Bojanowski P, Grave E, Joulin A, and Mikolov T
2017 {Enriching word vectors with subword information} 
arXiv:1607.04606v2

\bibitem{Bommannavar2014}
Bommannavar P, Kolcz A, Rajaraman A
2014 {Recall estimation for rare topic retrieval from large corpuses}
\emph{2014 IEEE International Conference on Big Data}

\bibitem{Yang2014}
Yang S, Kolcz A, Schlaikjer A, and Gupta P
2014 {Large--scale high-precision topic modeling on twitter} 
\emph{Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining} pp 1907--1916

\bibitem{Churikov2004} Churikov D V 2004
{Atomic functions and combined algorithm of image filtration in conditions of high intensity noise}
\emph{Radiotekhnika} \textbf{9} pp 69--71. In Russian.

\bibitem{Kravchenko2005}
Kravchenko V F, Fedorov I V, Churikov D V and Rvachev V L 2005 
{R--functions and the atomic functions in problems of complex--shaped contour objects description and digital image processing}
\emph{EW \& ES} \textbf{10} (7) pp 70--80. In Russian.
\end{thebibliography}

\end {document}

>>>>

\begin{abstract}
In this paper, the problem of constructing a model for detecting and filtering unwanted spam messages is solved. A fully connected convolutional neural network ({FCNN}) was chosen as the model of the classifier of unwanted emails in email. It allows you to divide emails into two categories: \emph{spam} and \emph{not spam}.
The main result of the research is a software application in the C++ language, which has a micro--service architecture and solves the problem of image classification. The app can handle more than $10^6$ requests per minute in real--time.
\end{abstract}

@@

\begin{table}[h!]
	\centering
	\caption{\label{tbl:01}Training result.}
	\begin{center}
		\begin{tabular}{lcc}
			\mr
			embeddings & precision & recall \\
			\mr
			BOW & 0.91143 & 0.99961 \\ \hline
			Fast Text & \bf 0.95523 & \bf 0.89164 \\ 
			\mr
		\end{tabular}
	\end{center}
\end{table}

@@

\begin{table}[h!]
	\centering
	\caption{\label{tbl:02}Training result.}
	\begin{center}
		\begin{tabular}{lcc}
			\mr
			embeddings & precision & recall \\
			\mr
			BOW & 0.93604 & 0.95643 \\ \hline
			Fast Text & \bf 0.99931 & \bf 0.91263 \\ 
			\mr
		\end{tabular}
	\end{center}
\end{table}

@@

\section*{References}
\begin{thebibliography}{99}
\bibitem{Makkar2021} 
Aaisha M, Uttam G and Pradip K S
2021 {Artificial intelligence and edge computing--enabled
web spam detection for next generation IoT
applications} {\it IEEE Sensors Journal} {\bf } 1--9

\bibitem{Taylor2020}
Taylor O E and Ezekiel P S
2020 {A model to detect spam email using support vector classifier and random forest classifier} 
\emph{Int. J. Comput. Sci. Math. Theory} {\bf 6} 1--11

\bibitem{Garg2021}
Pranjul G and Nancy G
2021 {A systematic review on spam filtering techniques based on
natural language processing framework} \emph{2021 11th International Conference on Cloud Computing, Data Science \& Engineering (Confluence 2021)} 30--35

\bibitem{Parmar2020}
Nandan P, Ankita S, Harshita J and Amol K K
2020 {Email spam detection using naïve Bayes and particle swarm optimization} \emph{Int. J. Inn. Res. Tech.} {\bf 6} 367--373

\bibitem{Mohammad2020}
Mohammad RMA
2020 {A lifelong spam emails classification model}
\emph{Appl. Comp. and Inf.} 1--20

\bibitem{Mikolov2013} 
Mikolov T, Chen K, Corrado G and Dean J
2013 {Efficient estimation of word representations in vector space} 
arXiv:1301.3781v3 1--12

\bibitem{Bojanowski2017} 
Bojanowski P, Grave E, Joulin A and Mikolov T
2017 {Enriching word vectors with subword information} 
arXiv:1607.04606v2 1--12

\bibitem{Bommannavar2014}
Bommannavar P, Kolcz A and Rajaraman A
2014 {Recall estimation for rare topic retrieval from large corpuses}
\emph{2014 IEEE International Conference on Big Data} 1--10

\bibitem{Yang2014}
Yang S, Kolcz A, Schlaikjer A and Gupta P
2014 {Large--scale high-precision topic modeling on twitter} 
\emph{Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining} 1907--1916

\bibitem{Churikov2004} Churikov D V 2004
{Atomic functions and combined algorithm of image filtration in conditions of high intensity noise}
\emph{Radiotekhnika} \textbf{9} 69--71. In Russian.

\bibitem{Kravchenko2005}
Kravchenko V F, Fedorov I V, Churikov D V and Rvachev V L 2005 
{R--functions and the atomic functions in problems of complex--shaped contour objects description and digital image processing}
\emph{EW \& ES} \textbf{10} 70--80. In Russian.
\end{thebibliography}
\end{document}
